A Technique for Inter-Retailer Recommendations

### 2014-06-11 paper2/paper.tex
Tweak discussion of popularity plot.

The third way in which popularity is used is determining the number
recommendations alotted per product. We assume that a popular product in one
catalogue is likely to be a popular product in another catalogue. Specifically,
the number of predicted inter-catalogue recommendations made per item is
made directly proportional to the item's value of $\rho$.

>>>>

The third way in which popularity is used is determining the number
recommendations alotted per product. We assume that a popular product in one
catalogue is likely to be a popular product in another catalogue. Specifically,
the number of predicted inter-catalogue recommendations predicted per item is
made directly proportional to the item's value of $\rho$.

This assumption is corroborated by the data. The following histogram shows the
number of gold-standard recommendations associated with the top 25 most popular
items, ranked by their value of $\rho$. The histogram also includes the
distribution of predicted recommendations for these items by the
$LatentFeatureRecommender$ both with and without popularity mechanisms. With
popularity, the predictions follow a similar distribution to that of the
gold-standard recommendations. Without popularity, the recommendations are
scattered more uniformly over the thousands of items of each catalogue such that
the number of times these 25 items are recommended is significantly smaller
(barely visible in the plot). This is because the recommendations are based
solely on similarity in concept space (after mapping) and popular items are not
inherently more similar to other items. Importantly, the
$LatentFeatureRecommender$ {\em without popularity} still outperforms the
$ContentBasedRecommender$ demonstrating that while popularity is important, it
is only one of several features that useful in choosing good inter-catalogue
recommendations.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible.}
    \label{fig:PopularityHistogram}
\end{figure}
